Approximation as Differentiation notes

### 2025-03-03 notes/sec/grothendieck.tex
Now I'm paying for the notation a bit...
Back to proof.#

\noindent In $\Fam(C)$ the objects $X$ are thus sets $\idx{X}$ paired with indexed families $\faml{X}$ in
$\Fam(\idx{X},C)$ and morphisms $f: X \to Y$ are functions $\idx{f}: \idx{X} \to \idx{Y}$ paired with
morphisms $\faml{f}: \faml{X} \to \reindex{\faml{Y}}{f}$ in $\Fam(\idx{X},C)$.

@@

\begin{enumerate}
\item $[X, Y]$ to be the object $(\Fam(C)(X,Y),[\idx{X}, \idx{Y}])$ in $\Fam(C)$ where $[\idx{X}, \idx{Y}]$
denotes the indexed family mapping every $f: X \to Y$ in $\Fam(C)$ to $\prod_{I}\reindex{Y}{\idx{f}}$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) sending any $f: X \times Y \to Z$ to
$\lambda_{X,Y,Z}(f): X \to [Y, Z]$ with:
\begin{itemize}
\item $\idx{\lambda}_{X,Y,Z}(f)(i) = g$ where $\idx{g}(j) = \idx{f}(i, j): \idx{Y} \to \idx{Z}$ and
$\faml{g}(j) = \faml{f}_{i,j} \comp \inj_{\faml{Y}_j}: \faml{Y}_i \to \faml{Z}_{\idx{f}(i, j)}$ where
$\inj_{\faml{Y}_j}: \faml{Y}_j \to \faml{X}_i \biprod \faml{Y}_j$
\item $\faml{\lambda}_{X,Y,Z}(f)(i) = \lambda_{\prod_{\faml{J}}}(j \mapsto \faml{f}_{i, j} \comp
\inj_{\faml{X}_i}: X_i \to \faml{Z}_{f(i,j)}$ where $\inj_{\faml{X}_i}: \faml{X}_i \to \faml{X}_i \biprod \faml{Y}_j$)
\end{itemize}
\item The family of morphisms $\eval_{X,Y}: [X, Y] \times X \to Y$ in $\Fam(C)$ with
\begin{itemize}
\item $\idx{\eval}_{X,Y}((f, g), i) = f(i)$
\item $\faml{\eval}_{X,Y}((f, g), i) = \coprodM{{\eval_{\prod}}_i}{g_i}: \prod_{I}\reindex{Y}{f} \biprod X_i \to Y_{f(i)}$
\end{itemize}
using $\coprodM{-}{-}$ to denote coproduct of morphisms.
\end{enumerate}
Then for any $f: X \times Y \to Z$ in $\Fam(C)$ we have \todo{(prove these)}:
\begin{enumerate}
\item The following diagram commutes:

>>>>

\noindent In $\Fam(C)$ the objects $X$ are thus sets $\idx{X}$ paired with indexed families $\faml{X}$ in
$\Fam(\idx{X},C)$ and morphisms $f: X \to Y$ are functions $\idx{f}: \idx{X} \to \idx{Y}$ paired with
morphisms $\faml{f}: \faml{X} \to \reindex{\faml{Y}}{\idx{f}}$ in $\Fam(\idx{X},C)$.

@@

\begin{enumerate}
\item $[X, Y]$ to be the object $(\Fam(C)(X,Y),[\idx{X}, \idx{Y}])$ in $\Fam(C)$ where $[\idx{X}, \idx{Y}]$
denotes the indexed family mapping every $f: X \to Y$ in $\Fam(C)$ to
$\prod_{\idx{X}}\reindex{\faml{Y}}{\idx{f}}$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) sending any $f: X \times Y \to Z$ to
$\lambda_{X,Y,Z}(f): X \to [Y, Z]$ with:
\begin{itemize}
\item $\idx{\lambda}_{X,Y,Z}(f)(i) = g$ where $\idx{g}(j) = \idx{f}(i, j): \idx{Y} \to \idx{Z}$ and
$\faml{g}(j) = \faml{f}_{i,j} \comp \inj_{\faml{Y}_j}: \faml{Y}_i \to \faml{Z}_{\idx{f}(i, j)}$ where
$\inj_{\faml{Y}_j}: \faml{Y}_j \to \faml{X}_i \biprod \faml{Y}_j$
\item $\faml{\lambda}_{X,Y,Z}(f)(i) = \lambda_{\prod_{\faml{J}}}(j \mapsto \faml{f}_{i, j} \comp
\inj_{\faml{X}_i}: \faml{X}_i \to \faml{Z}_{f(i,j)}$ where $\inj_{\faml{X}_i}: \faml{X}_i \to \faml{X}_i
\biprod \faml{Y}_j$)
\end{itemize}
\item The family of morphisms $\eval_{X,Y}: [X, Y] \times X \to Y$ in $\Fam(C)$ with
\begin{itemize}
\item $\idx{\eval}_{X,Y}((f, g), i) = f(i)$
\item $\faml{\eval}_{X,Y}((f, g), i) = \coprodM{{\eval_{\prod}}_i}{g_i}: \prod_{\idx{X}}\reindex{\faml{Y}}{f}
\biprod \faml{X}_i \to \faml{Y}_{f(i)}$
\end{itemize}
using $\coprodM{-}{-}$ to denote coproduct of morphisms.
\end{enumerate}
Then for any $f: X \times Y \to Z$ in $\Fam(C)$ we have \todo{(prove these)}:
\begin{enumerate}
\item The following diagram commutes:
